In-Rank mesh optimization for URL customized promotion in SEO

### 2015-04-29 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag
last version

  search engine optimization, e-commerce, page rank, in rank, mesh optimization, global optimization, Hadoop, Spark GraphX, Neo4j

@@

  First the universe we deal with is discrete and vast. For a mesh with $N$ nodes (a site with $N$ URLs), the number of possible meshes is $2^{N^{2}}$. 

@@

  Not only optimum existence and uniqueness results are inexistent, but those problems usually reveal to be computationnaly intensive to solve. 
  For our case, exhaustive optimization would be far too computationally intensive. We have to find a proper heuristic based global optimization algorithm to cleverly tweak through our universe.

@@

  But of course, as heuristic, this algorithm must not be trusted : it might get stuck into local minima, depend upon initial set-up and randomness stream seed. 
  Parameters also have to be properly tweaked to proceed through our universe avoiding getting stuck into local minima.

@@

  is also relevant as most e-commerce sites dedicate specific zones for links to similar products, list of products and so on.
  So links can only be created within certain categories of pages and zones within our page. In other terms our mesh will not be totally free and 

@@

  or we try not to reinvent the wheel and plug ourselves to existing big data cluster platform. We'll here detail our technological choices.

@@

  f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R} \\

@@

  Let's $$\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$$ denote the adjacency matrix of our directed graph.

@@

  $\left(G_{ij}\right)$ is either 1 or 0 if there is a link between URL $i$ and $j$.

@@

  In our case, each individual or chromosome $\left(C_{i}\right)  \in \left\{0,1\right\}^{N\times N}$ here represented as a bits array, which results from the vectorization of
  the adjacency matrix $\left(G_{ij}\right)$. An individual is a specific mesh.

  At each generation, a candidate can either result from a crossover between two parents or from a self mutation.

@@

  The newly created mutant also shares many of the characteristics of its parent. 
  The mutation function is even simpler : we just switch bits whose locations are randomly chosen
  and proportions equal a fixed mutation rate : 

@@

  Let's add here that taking account our mesh constraints is here trivial : we just fix the value of blocs of links between forbidden categories from our
  vector. We just end up with a vector with a smaller number of freedom degrees : our adjacency matrix is square but with large fixed null blocks resulting only from locations where links can be added.

@@

  to push forward pages accordingly to an prominence metrics which is yours to define. The difficulty here does not lie in the

>>>>

  search engine optimization, e-commerce, page rank, in rank, mesh optimization, global optimization, tf/idf, Levenshtein, Hadoop, Spark GraphX, Neo4j

@@

  First the universe we deal with is discrete and vast. For a mesh with $N$ nodes (a site with $N$ URLs), the number of possible meshes (directed graph) is $2^{N^{2}}$. 

@@

  Not only optimum existence and uniqueness results are inexistent, but those problems appear generally to be computationnaly intensive to solve. 
  For our case, exhaustive optimization would be far too computationally intensive. We have to find a proper heuristic based global optimization algorithm to cleverly browse through our universe.

@@

  But of course, as heuristic, this algorithm must not be trusted : it can get stuck into local minima and results will depend upon initial set-up and randomness stream seed. 
  Parameters also have to be properly tweaked to proceed through our universe to avoid getting stuck into local minima.

@@

  is also relevant as most e-commerce sites dedicate specific zones for links to similar products, filtered lists and so on. Siloing navigation will also forbid links between distinct universe.
  So links can only be created within certain categories of pages and zones within those pages. In other terms our mesh will not be totally free and 

@@

  or we try not to reinvent the wheel and plug ourselves to existing big data cluster platforms. We'll here detail our technological choices.

@@

  f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\

@@

  Let's $$\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$$ denote the vectorized adjacency matrix of our directed graph.

@@

  $\left(G_{ij}\right)$ is either 1 or 0 if there is a link between URL $i$ and $j$ and our matrix is reshaped into a vector by concatenating each row.

@@

  In our case, each individual or chromosome $\left(C_{i}\right)  \in \left\{0,1\right\}^{N\times N}$ here is represented as a bits array, which results from the very vectorization of
  our adjacency matrix $\left(G_{ij}\right)$. An individual is a specific mesh.

  At each generation, a candidate can either results from a crossover between two parents or from a self mutation.

@@

  The newly created mutant also shares many of the characteristics of its single parent. 
  The mutation function is here standard : we just switch bits whose locations are randomly chosen
  and proportions equal a fixed defined mutation rate $\alpha$ : 

@@

  Let's add here that taking into account our mesh constraints is here trivial : we just fix the value of blocs of links between forbidden categories from our
  vector. We just end up with a vector with a smaller number of freedom degrees : our adjacency matrix is square but with large fixed null blocks resulting only from locations where links can't be added.

@@

  to push forward pages accordingly to a prominence metrics which is yours to define. The difficulty here does not lie in the
